Algebraic properties of CFT coset construction and Schramm-Loewner evolution

### 2011-10-17 AffineLieAlgebras/SLE/article.tex
Minor changes in sle paper

>>>>

\subsection{Semisimple Lie algebras and coset construction}
\label{sec:semis-lie-algebr}

It is well known that unitary minimal models with central charge $c=1-\frac{6}{m(m+1)}$ can be obtained from coset construction starting with $su(2)_{m}\oplus su(2)_{1}$ WZW-model and factorizing it by $su(2)_{m+1}$. Here lower index represents level of affine Lie algebra representation.

In this case the dimension of Lie algebra $\gf=su(s)\oplus su(2)$ is 6, dual Coxeter number $h^{v}=2+2=4$.

\begin{equation*}
  \left| \psi\right>=\left(-2 L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau\sum_{a} J^{a}_{-1} J^{a}_{-1}\right) \left|\phi_{\Lambda}\right>    
\end{equation*}

SLE and factorization by equivalence relations.
